Penalized linear mixed models for structured genetic data

### 2021-03-15 lmm-genetic-review.tex
Fixing missing \real def for "plain" article
adding renamed figures per journal guidelines

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{comment}
\usepackage{float}
\usepackage{color}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tkz-euclide}
\usepackage{lscape}

@@

% Tikz settings optimized for causal graphs.
% Just copy-paste this part
\usetikzlibrary{shapes,decorations,decorations.markings,arrows,calc,arrows.meta,fit,positioning}
\tikzset{
    -Latex,auto,node distance =1 cm and 3 cm,semithick,
    state/.style ={ellipse, draw, minimum width = 0.7 cm},
    point/.style = {circle, draw, inner sep=0.04cm,fill,node contents={}},
    bidirected/.style={Latex-Latex,dashed},
    el/.style = {inner sep=2pt, align=left, sloped},
    strike through/.append style={
    decoration={markings, mark=at position 0.5 with {
    \draw[-] ++ (-4pt,-4pt) -- (4pt,4pt);}
  },postaction={decorate}}
}

\usepackage{subcaption}
\usepackage{url}
\allowdisplaybreaks
\usepackage{natbib}
%\usepackage{biblatex}
%\AtEveryCitekey{%
%  \clearfield{note}%
%}
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\usetikzlibrary{arrows}
\providecommand{\pb}[1]{\textcolor{red}{#1}}
\providecommand{\anna}[1]{\textcolor{blue}{#1}}
\newcommand{\bbeta}[1][]{\boldsymbol{\beta}{#1}}
\newcommand{\bbetaT}{\widetilde{\boldsymbol{\beta}}}
\newcommand{\bbetaHat}[1][]{\widehat{\boldsymbol{\beta}{#1}}}
\newcommand{\bgamma}{\boldsymbol{\gamma}}
\newcommand{\beps}[1][]{\boldsymbol{\varepsilon}{#1}}
\newcommand{\bepsT}[1][]{\widetilde{\boldsymbol{\varepsilon}{#1}}}
\newcommand{\bD}{\mathbf{D}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bK}{\mathbf{K}}
\newcommand{\bI}{\mathbf{I}}
\renewcommand{\P}{\mathbf{P}}
\newcommand{\bR}{\mathbf{R}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bZ}{\mathbf{Z}}
\newcommand{\bXT}{\widetilde{\mathbf{X}}}
\newcommand{\byT}{\widetilde{\mathbf{y}}}
\newcommand{\bZT}{\widetilde{\mathbf{Z}}}
\newcommand{\sigmaee}{\sigma^2_e}
\newcommand{\sigmagg}{\sigma^2_g}
\newcommand{\T}{\text{T}}
\newcommand{\lam}{\lambda}

\title{A comparative analysis of penalized linear mixed models in structured genetic data}
\author{Anna Reisetter \qquad Patrick Breheny\\
  Department of Biostatistics\\University of Iowa}
\date{\today}

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{comment}
\usepackage{float}
\usepackage{color}
%\usepackage{tikz}
%\usepackage{tikz-cd}
\usepackage{tkz-euclide}
\usepackage{lscape}
%%% UNCOMMENT THIS WHEN DONE EDITING TO PUT FIGS AT END
%\usepackage{endfloat}
\usepackage{epstopdf}

@@

\usepackage{subcaption}
\usepackage{url}
\allowdisplaybreaks
\usepackage{natbib}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\providecommand{\pb}[1]{\textcolor{red}{#1}}
\providecommand{\anna}[1]{\textcolor{blue}{#1}}
\newcommand{\bbeta}[1][]{\boldsymbol{\beta}{#1}}
\newcommand{\bbetaT}{\widetilde{\boldsymbol{\beta}}}
\newcommand{\bbetaHat}[1][]{\widehat{\boldsymbol{\beta}{#1}}}
\newcommand{\bgamma}{\boldsymbol{\gamma}}
\newcommand{\beps}[1][]{\boldsymbol{\varepsilon}{#1}}
\newcommand{\bepsT}[1][]{\widetilde{\boldsymbol{\varepsilon}{#1}}}
\newcommand{\bD}{\mathbf{D}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bK}{\mathbf{K}}
\newcommand{\bI}{\mathbf{I}}
\renewcommand{\P}{\mathbf{P}}
\newcommand{\bR}{\mathbf{R}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bZ}{\mathbf{Z}}
\newcommand{\bXT}{\widetilde{\mathbf{X}}}
\newcommand{\byT}{\widetilde{\mathbf{y}}}
\newcommand{\bZT}{\widetilde{\mathbf{Z}}}
\newcommand{\sigmaee}{\sigma^2_e}
\newcommand{\sigmagg}{\sigma^2_g}
\newcommand{\sigmass}{\sigma^2_s}
\newcommand{\T}{\text{T}}
\newcommand{\lam}{\lambda}
\providecommand{\real}{\mathbb{R}}

\title{Penalized linear mixed models for structured genetic data}
\author{Anna Reisetter \qquad Patrick Breheny\\
  Department of Biostatistics\\University of Iowa}
\date{\today}
